The Fates of Merging Supermassive Black Holes and a Proposal for a New Class of X-Ray Sources

### 2020-01-12 paper.tex
Last commit before changing accretion rate methodology.

\subsection{Simulation setup}
For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined from \citet{2008gady.book.....B} as:
\begin{equation}\label{tfric}
    t_{fric} = \frac{19}{6}\left(\frac{R_\mathrm{e}}{5\mathrm{kpc}}\right)^2\frac{\sigma(R_\mathrm{e})}{200\mathrm{km}\,\mathrm{s}^{-1}}\frac{10^8\,M_{\odot}}{M_\mathrm{BH}} \text{  Gyr},
\end{equation}
The orbiting black holes were injected into their host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.  Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{GM(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.

@@

\subsection{Black Hole Luminosity}
The x-ray temperature versus central velocity dispersion relation from Table 2 of  \citet{2018ApJ...857...32B} was fitted according to:
\begin{equation}
    T_x = 10^{2.50*log(\sigma_c) - 6.06} \text{  keV}.
\end{equation}
Central gas density, ${\rho}_0$ was also fitted from Table 3 of \citet{2018ApJ...857...32B} according to:
\begin{equation}
    \rho_0 = 10^{0.6*log(\sigma_c) - 25} \text{  g cm}^{-3}.
\end{equation}
The core radius of the gas model, ${r_c}$ is:
\begin{equation}
    r_c = 10^{2.1*log(\sigma) - 5.3} \text{  kpc}.
\end{equation}
Local gas density ${\rho}$ is obtained from the isothermal beta model (\citet{1962AJ.....67..471K}, \citet{1976A&A....49..137C}, \citet{1978A&A....70..677C}):
\begin{equation} \label{beta_model}
    \rho = \frac{\rho_0}{(1+r^2/r_c^2)^{1.5}} \text{  g cm}^{-3}.
\end{equation}

@@

Finally, the black hole x-ray luminosity is estimated from:
\begin{equation}
    L_x = \epsilon_{rx}\dot{M}_{acc}c^2 \text{  erg s}^{-1},
\end{equation}
where the x-ray radiative efficiency ${\epsilon}_{rx}=0.01$, and we are assuming for the low-luminosity sources that $L_B{\sim}L_x$.  For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$.
The Eddington limit is defined as:
\begin{equation}
    L_{edd} = 1.26 \times 10^{38} (M/M_{\odot}) \text{  erg s}^{-1}.
\end{equation}

>>>>

\subsection{Simulation setup}\label{subsec:simset}
For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined from \citet{2008gady.book.....B} as:
\begin{equation}\label{tfric}
    t_{fric} = \frac{19}{6}\left(\frac{R_\mathrm{e}}{5\mathrm{kpc}}\right)^2\frac{\sigma(R_\mathrm{e})}{200\mathrm{km}\,\mathrm{s}^{-1}}\frac{10^8\,M_{\odot}}{M_\mathrm{BH}} \text{  Gyr},
\end{equation}
The orbiting black holes were injected into their host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.  Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{GM(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.

@@

\subsection{Black Hole Xray Luminosity}
\subsubsection{Calculations}
As a black hole traverses through a host galaxy or other gaseous environment, it accretes

The x-ray temperature versus central velocity dispersion relation from Table 2 of  \citet{2018ApJ...857...32B} was fitted according to:
\begin{equation}
    T_x = 10^{2.50*log(\sigma_c) - 6.06} \text{  keV}.
\end{equation}
Central gas density, ${\rho}_0$ was also fitted from Table 3 of \citet{2018ApJ...857...32B} according to:
\begin{equation}
    \rho_0 = 10^{0.6*log(\sigma_c) - 25} \text{  g cm}^{-3}.
\end{equation}
The core radius of the gas model, ${r_c}$ is:
\begin{equation}
    r_c = 10^{2.1*log(\sigma) - 5.3} \text{  kpc}.
\end{equation}
Local gas density ${\rho}$ is obtained from the isothermal beta model (\citet{1962AJ.....67..471K}, \citet{1976A&A....49..137C}, \citet{1978A&A....70..677C}):
\begin{equation} \label{beta_model}
    \rho = \frac{\rho_0}{(1+r^2/r_c^2)^{1.5}} \text{  g cm}^{-3}.
\end{equation}

@@

Finally, the black hole x-ray luminosity is estimated from:
\begin{equation}
    L_x = \epsilon_{rx}\dot{M}_{acc}c^2 \text{  erg s}^{-1},
\end{equation}
where the x-ray radiative efficiency ${\epsilon}_{rx}=0.01$, and we are assuming for the low-luminosity sources that $L_x{\sim}L_{Bol}$.  For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$.
The Eddington limit is defined as:
\begin{equation}
    L_{edd} = 1.26 \times 10^{38} (M/M_{\odot}) \text{  erg s}^{-1}.
\end{equation}
